% This file was converted to LaTeX by Writer2LaTeX ver. 0.4b
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass[12pt,twoside]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{calc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue}
% List styles
\newcommand\liststyleLi{%
\renewcommand\labelitemi{{\textbullet}}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{{\textbullet}}
}
% Pages styles (master pages)
\makeatletter
\newcommand\ps@Standard{%
\renewcommand\@oddhead{}%
\renewcommand\@evenhead{}%
\renewcommand\@oddfoot{}%
\renewcommand\@evenfoot{}%
\setlength\paperwidth{20.999cm}\setlength\paperheight{29.699cm}\setlength\voffset{-1in}\setlength\hoffset{-1in}\setlength\topmargin{2cm}\setlength\headheight{12pt}\setlength\headsep{0cm}\setlength\footskip{12pt+0cm}\setlength\textheight{29.699cm-2cm-2cm-0cm-12pt-0cm-12pt}\setlength\oddsidemargin{2cm}\setlength\textwidth{20.999cm-2cm-2cm}
\renewcommand\thepage{\arabic{page}}
\setlength{\skip\footins}{0.101cm}\renewcommand\footnoterule{\vspace*{-0.018cm}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}
}
\makeatother
\pagestyle{Standard}
\begin{document}
{\bfseries
Introduction to Artificial Neural Network Editor (ANNE)}


\bigskip

{
The initial description for the project was as follows:

{\textit{
The aim of this project is to build a flexible tool for building large
scale neural network models of aspects of brain functioning. The tool
will allow the user to specify what the function of an individual
neuron is, what the overall connectivity of the neurons is, and will
then build the corresponding network and allow simulations to be run on
it.}}

There are three obvious key requirements from the initial description
which are:

\begin{itemize}
\item 
{
Flexibility {--} The tool must be able to work with a number of
different neural network paradigms, in response to this we designed our
solution to be highly modular and pluggable with further extensions
which would require no changes to be made to the core framework.
}
\item 
{
High Detail Modelling {--} Users should be able to manipulate individual
neurons and their connectivity which is simple enough, however with the
scale of networks desired performance issues arrive. The framework was
designed to handle large networks from the outset enabling the best
possible performance.
}
\item 
{
Build and Simulate networks {--} The ability to run and train networks,
as well as export them to an intermediate language, which NeuroML was
chosen to be the modelling standard implemented. Spike Time Dependent
Plasticity (STDP) was implemented for network training as well as a
number of network execution features and data output features.
}
\end{itemize}

Neural Networks are involved in a number of areas of
research, especially within Artificial Intelligence in Computer
Science. Neural Networks have the ability to learn relatively complex
functions that can range from simple logical operators, such as
{\textit{AND, OR}} and
{\textit{XOR}} to facial and emotion
recognition from photographs or facial markers.

Neural networks are made up of two main features, Neurones, which are
nodes in a graph and Synapses which are the edges. Nodes take an input
from other nodes across synapses which may themselves have properties
such as weight or delay, neurones then perform a function on the
inputs, perhaps with their own bias before sending that information
through the \ graph. Neural networks can operate over iterations where
information is sent from the start to the end, or in a timed fashion
where information is sent through but takes time to travel through the
network. Artificial neural networks generally work with a more
arbitrary value being passed through the network were Biologically
inspired neural networks work with voltages and thresholds more
commonly. Biologically inspired networks, as you might expect try to
model neural networks as closely as possible to those found within
biological systems.

One area where our solution is hopefully going to
receive some use is with the iCub robot that the Department of
Computing, Imperial College London has recently taken possession of.
The iCub is a sophisticated robot which is designed to have the
proportions and movement of a 3.5 year old child, the main goal of the
iCub project, which is run by the RobotCub Consortium
is to study cognition through the implementation of biologically
motivated algorithms.

This is why there is an emphasis within the ANNE towards biological
networks which include neurones such as Excitatory and Inhibitory
Spiking Neurones. ANNE also supports more artificially inspired
networks as well, but because of the pluggable nature of ANNE, adding
support for new Neurones or Synapses is possible, hopefully extending
the useful life time of the application without the need for waiting
for new release cycles to complete and allow other developers to extend
and focus the tool to their own requirements.

Overall, ANNE provides a simple and intuitive user interface which gives
the user a high degree of control of designing, training and executing
large scale networks. It gives developers a solid framework which is
highly pluggable making application extensions trivial to integrate and
distribute, giving ANNE a longer lifetime and the ability with
extensions to model new network paradigms.
}
\end{document}
