% This file was converted to LaTeX by Writer2LaTeX ver. 0.4b
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass[12pt,twoside]{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{calc}
\usepackage{longtable}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue}
% List styles
\newcommand\liststyleLi{%
\renewcommand\labelitemi{{\textbullet}}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{{\textbullet}}
}
\newcommand\liststyleLii{%
\renewcommand\labelitemi{{\textbullet}}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{{\textbullet}}
}
\newcommand\liststyleLiii{%
\renewcommand\labelitemi{{\textbullet}}
\renewcommand\labelitemii{${\circ}$}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{{\textbullet}}
}
% Pages styles (master pages)
\makeatletter
\newcommand\ps@Standard{%
\renewcommand\@oddhead{plc06 / jv06 / ctm06 / ig106 / sjw06\hfill \hfill Artificial Neural Network Editor (ANNE) Report}%
\renewcommand\@evenhead{\@oddhead}%
\renewcommand\@oddfoot{\hfill Page \thepage{} of ?}%
\renewcommand\@evenfoot{\@oddfoot}%
\setlength\paperwidth{20.999cm}\setlength\paperheight{29.699cm}\setlength\voffset{-1in}\setlength\hoffset{-1in}\setlength\topmargin{2cm}\setlength\headheight{12pt}\setlength\headsep{0.499cm}\setlength\footskip{12pt+0.499cm}\setlength\textheight{29.699cm-2cm-2cm-0.499cm-12pt-0.499cm-12pt}\setlength\oddsidemargin{2cm}\setlength\textwidth{20.999cm-2cm-2cm}
\renewcommand\thepage{\arabic{page}}
\setlength{\skip\footins}{0.101cm}\renewcommand\footnoterule{\vspace*{-0.018cm}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
% footnotes configuration
\makeatletter
\renewcommand\thefootnote{\arabic{footnote}}
\makeatother
\everymath{\displaystyle}
\begin{document}
{\bfseries
Persistence Overview}

{\mdseries
}

\begin{center}
\begin{minipage}{10cm}
{\raggedleft\itshape
 [Warning: Image not found] Illustration 1:
Persistence's location within the framework.
\par}
\end{minipage}\end{center}
{\mdseries
Illustration 1 provides a view of how persistence is located within the
framework, its dependencies and modules that depend on it. Obviously
the user interface is dependent on the persistence module being present
for the ability to save or load neural networks which have been
designed within the application. Persistence depends on the model of
these networks, a few core utilities and events for serialization and
de{}-serialization of networks. This is coherent with the low coupling
design of the framework.}


\bigskip

{\mdseries
}

\begin{center}
\begin{minipage}{17cm}
{\raggedleft\itshape
 [Warning: Image not found] Illustration 2: Persistence Modules
Implementation.
\par}
\end{minipage}\end{center}
{\mdseries
Illustration 2 is an overview of all the classes and interfaces within
the Persistence module and their package separation. XML and TNS have
their own packages as they required specific classes for their
implementation, where Java Serialization makes use of the in built Java
ability to serialization objects to a persistable storage location, X3D
is dependent on XML but required no other classes apart from its own
for its persistence.}

\clearpage{\bfseries
Persistence Design}

{\mdseries
The persistence layer has been designed like many aspects of the
application to be completely plug{}-able with new extension, adding a
plug{}-in requires no existing code to be changed and your new
plug{}-in to extend the \textit{SaveService}\textup{ for saving
networks and }\textit{LoadService}\textup{ for loading networks, these
abstract classes provide the method headers for creating persistence
services. A new plug{}-in doesn't have to implement
both loading and saving, as in the case with the X3D service which is
only available for exporting networks too.}}

{\mdseries\upshape
}

\begin{center}
\begin{minipage}{10cm}
{\raggedleft\itshape
 [Warning: Image not found] Figure 1: View of Open Dialogue, Available
files are highlighted.
\par}
\end{minipage}\end{center}
{\mdseries\upshape
A number of persistence plug{}-ins are provided with the standard
distribution, they are:}

\liststyleLi
\begin{itemize}
\item \textmd{\textit{Java
Serialization}}\footnote{ttp://java.sun.com/j2se/1.4.2/docs/api/java/io/Serializable.html}\textmd{\textup{
{--} the network is serialized using the Java Serializable interface,
this is used as the default persistence option and preferred over the
other modules, especially when not transporting the neural network to
another application. This is because it is extremely fast and
guarantees that all information is persisted and that will be able to
be loaded again. As the serialized network is the actual objects of our
implementation, the only applications that would be able to make use of
this format is one which uses our classes for network representation.
Files are given the }}\textmd{\textit{.net}}\textmd{\textup{
extension.}}
\item {\itshape
\textmd{NeuroML}\footnote{http://www.neuroml.org/}\textmd{
(XML)}\textmd{\textup{ {--} this is the main persistence module for
exporting to a number of other applications that also support the
NeuroML Layer 3 Network Schema for representing in neural networks.
Import is also supported for taking NeuroML for other applications that
also use this schema, allowing for some cross{}-application
computability. The XML that is generated is well{}-formed and NeuroML
validated, meaning that other applications should accept this format
without errors. Files are given the }}\textmd{.xml}\textmd{\textup{
extension.}}}
\item {\itshape
\textmd{TextNetworkSerializer}\textmd{\textup{ {--} is a simple export
and import specification which outputs records of all the objects into
ASCII format for storage, it is however a non{}-standard format which
is only implemented by our application so it cannot be used for
exporting to or importing from other application. It does however have
a low storage overhead compared to XML as records are separated by new
lines and values by commas. Files are given the
}}\textmd{.tns}\textmd{\textup{ extension.}}}
\item {\itshape
\textmd{X3D}\textmd{\textup{ {--} is a royalty{}-free open standards
file format and run{}-time architecture to represent and communicate 3D
scenes and objects using
XML}}\footnote{http://www.web3d.org/about/overview/}\textmd{\textup{.
We implemented only an export feature to X3D as applications that
implement this standard are designed for viewing, not modelling items,
also the feature is implemented by an XSL transformation from our
NeuroML that is generated and we chose not to implement an XSLT for
transforming from X3D to NeuroML. Files are given the
}}\textmd{.x3d}\textmd{\textup{ extension.}}}
\end{itemize}

\bigskip

{\itshape
\textmd{\textup{Further plug{}-ins for persistence which would expand
the project could include
PyNN}}\footnote{http://neuralensemble.org/trac/PyNN/}\textmd{\textup{
and the Neural Network Tool within
Matlab}}\footnote{http://www.mathworks.com/access/helpdesk/help/toolbox/nnet/index.html}\textmd{\textup{.}}}

\clearpage{\bfseries\upshape
Persistence Implementation}

{\mdseries\upshape
As previously mentioned with the highly pluggable architecture, loading
and saving is abstract out as far as possibly into plug{}-ins, all
loading and saving is handled by their respective managers which is the
last point in the chain of the core system before becoming plug{}-ins.
Its the managers job to take a load or save specification which
includes information about where to write or read too and also which
plug{}-in to use to perform the persistence operation. The manager then
loads the required plug{}-in before making the appropriate method
calls.}


\bigskip

{\mdseries\itshape
\textup{Networks must be saveable and/or serializable to be used with
the }SaveManager \textup{and save plug{}-ins, further still any object
that has parameters or variables that require being persisted to
storage must have them annotated with the annotation
}@persistable\textup{, this is for when an object is being persisted
it, reflection can be used to retrieve all information from the object
that needs to be exported. It is also used when loading persisted
information and populating information in objects when they are created
on reading a persisted network.}}


\bigskip

{\mdseries\upshape
Serialization was the simplest implementation as it makes use of
Java's ability to serialize objects to file and allow
them to be read back in, as the loading plug{}-ins are used for when a
user wishes to insert a network from file into one which they are
editing currently, after the network is loaded, objects must have their
Ids regenerated to prevent Id conflictions.}


\bigskip

{\mdseries\upshape
TNS and NeuroML are implemented in a very similar way, the some
difference is when information is output, NeuroML has to conform to the
NeuroML schema, which specifies that networks and their neurones must
be output and then the synapses, TNS outputs objects as it gets them.
This requires NeuroML to buffer some information so that it can be
output at the correct time. NeuroML does a breadth first search of the
network to discover all the networks and network bridges that are in
the network being persisted.}


\bigskip

{\mdseries\itshape
\textup{Importing TNS and NeuroML is more interesting, TNS read each
line of the file, as each record is a single line, and then can form
the complete object as all the information is provided within the
record, this can then be used when all the information has been loaded
and objects created to link up the whole network before returning the
completed network. With the NeuroML however information is note only
stored in a single tag, but multiple tags, including meta{}-data tags,
this requires more information to be stored and lead to the
}PartialObject\textup{ idea, which stores information until completed
and then will produce the desired object with parameters set as it
knows. More information needed to be stored because the XML parser that
was used to read the XML was SAX (Simple API for
XML)}\footnote{http://www.saxproject.org/}\textup{ SAX is event driven
and dependent on what the parser has read at that time is what you
receive. So depending on the type of tag seen, if it is an opening tag
for a neurone, network or synapse then a partial object is placed on a
stack, as further meta{}-data seen is relevant to the last seen partial
object. Then on closing tags for neurone, network or synapse, the
partial object creates the complete object based on the parameters that
it has stored and returns it. At the end of the document the network is
connected up with sub{}-networks and the final network can be
retrieved. Objects that require methods to be called other than the
standard constructer when being loaded from persisted storage may
create methods that are persistable but have no value, so that they are
called when loaded, any further method calls can be placed within that
single public }}


\bigskip

{\bfseries\itshape
\textmd{\textup{X3D is currently depended on the XML persistence
plug{}-in as the network must first be exported to XML, the XML file is
then read and an extensible style sheet (XSL) is applied to the XML to
transform it to the X3D schema. X3D persistence was implemented this
way because it was a quick addition as the XSL was already available
from the NeuroML
project}}\footnote{http://www.neuroml.org/NeuroMLValidator/NeuroMLFiles/Schemata/v1.7.2/Level3/NeuroML\_Level3\_v1.7.2\_X3D.xsl}\textmd{\textup{.
This implementation is not ideal as it makes use of the Java XML
libraries}}\footnote{http://java.sun.com/j2se/1.5.0/docs/api/javax/xml/transform/Transformer.html}\textmd{\textup{,
which has problems when applying an XSL transformation to a large XML
document, which is why in Persistence Performance Analysis no data is
available for save execution time and file size for X3D documents with
a node count over 100. Dependencies on other plug{}-ins is resolved by
the Plug{}-in Manager and so not an issue for the Persistence
Module.}}}

\clearpage{\bfseries\upshape
Persistence Examples}

{\mdseries\upshape
For reference, across the following pages are examples of an exported
network in NeuroML, TNS and X3D, Java serialization
wasn't included as it is not a human readable form.}


\bigskip

{\mdseries\upshape
The example network is two Excitatory Spiking Neurones with synapses to
each other and themselves (otherwise known as 100\% connectivity). A
view of the network in the ANNE tool is shown below:}


\bigskip

{\upshape
}

\begin{center}
\begin{minipage}{17cm}
{\raggedleft\itshape
 [Warning: Image not found] Figure 2: View of the example network in
ANNE.
\par}
\end{minipage}\end{center}
{\upshape
It is easy to see that the TNS output is very light but hard to
interpret by reading, on the contrary, both the XML formats \ are very
long but very intuitive to read. Its also clear that the X3D output has
lost a large amount of information on the neural network, which is the
main reason why no importer for X3D was written.}


\bigskip

{\upshape
}

\begin{center}
\begin{minipage}{10.06cm}
{\raggedleft\itshape
 [Warning: Image not found] Figure 3: View of a Network produced in ANNE
displayed in Octaga.
\par}
\end{minipage}\end{center}
{\upshape
Above is an example of the X3D output from ANNE being loaded into an X3D
viewer called Octaga\footnote{http://www.octaga.com}. This allows users
to view their networks in 3D if they find that feature useful and
demonstrates some of the inter{}-application support within ANNE.}


\bigskip

\begin{longtable}[c]{|p{14.8cm}|}
\hline
{\sffamily
\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}?xml}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.2,0.47843137,0.5294118}{version}}\texttt{\textcolor{black}{=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.2,0.47843137,0.5294118}{encoding}}\texttt{\textcolor{black}{=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}UTF{}-8{\textquotedbl}}}\texttt{\textcolor{black}{?}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}}

\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{networkml
xmlns=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}http://morphml.org/networkml/schema{\textquotedbl}}}

\texttt{\textcolor{black}{\ \ xmlns:xsi=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}http://www.w3.org/2001/XMLSchema{}-instance{\textquotedbl}}}

\texttt{\textcolor{black}{\ \ xmlns:meta=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}http://morphml.org/metadata/schema{\textquotedbl}}}

\texttt{\textcolor{black}{\ \ xsi:schemaLocation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}http://morphml.org/networkml/schema/Schemata/v1.7.3/Level3/NetworkML\_v1.7.3.xsd{\textquotedbl}}}

\texttt{\textcolor{black}{lengthUnits=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}micron{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:notes}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}\texttt{\textcolor{black}{Produced
by ANNE: the Artifical Neural Network
Editor}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:notes}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{populations}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{population
name=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}14{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{instances
size=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{instance
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}16{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.SpikingNeurone{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}postSpikeReset{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}{}-56.17718294810968{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}z{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}recoverySensitivity{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.2{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}recoveryScale{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.02{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}x{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}73{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}trigger{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}30.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}charge{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}{}-65.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}y{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}26{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}pSRRecovery{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}4.0027868923975625{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{location
x=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}73{\textquotedbl}}}\texttt{\textcolor{black}{
y=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}26{\textquotedbl}}}\texttt{\textcolor{black}{
z=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{instance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{instance
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}15{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.SpikingNeurone{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}postSpikeReset{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}{}-58.618716832163614{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}z{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}recoverySensitivity{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.2{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}recoveryScale{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.02{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}x{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}456{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}trigger{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}30.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}charge{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}{}-65.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}y{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}292{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}pSRRecovery{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}4.551832219630733{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{location
x=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}456{\textquotedbl}}}\texttt{\textcolor{black}{
y=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}292{\textquotedbl}}}\texttt{\textcolor{black}{
z=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{instance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{instances}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{population}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{populations}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{projections
units=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Physiological
Units{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{projection
name=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Network{}-Synapses{\textquotedbl}}}\texttt{\textcolor{black}{
source=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}14{\textquotedbl}}}\texttt{\textcolor{black}{
target=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}14{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{synapse\_props
synapse\_type=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.Synapse{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{connections
size=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}4{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{connection
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}17{\textquotedbl}}}\texttt{\textcolor{black}{
pre\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}16{\textquotedbl}}}\texttt{\textcolor{black}{
post\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}16{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{properties
weight=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.8604082982707334{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.Synapse{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{connection}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{connection
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}20{\textquotedbl}}}\texttt{\textcolor{black}{
pre\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}15{\textquotedbl}}}\texttt{\textcolor{black}{
post\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}15{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{properties
weight=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.5024901465406223{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.Synapse{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{connection}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{connection
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}18{\textquotedbl}}}\texttt{\textcolor{black}{
pre\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}16{\textquotedbl}}}\texttt{\textcolor{black}{
post\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}15{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{properties
weight=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.270062017417825{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}
}}\texttt{\textcolor{black}{value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.Synapse{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{connection}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{connection
id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}19{\textquotedbl}}}\texttt{\textcolor{black}{
pre\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}15{\textquotedbl}}}\texttt{\textcolor{black}{
post\_cell\_id=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}16{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{properties
weight=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.13243622803794775{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{meta:property
tag=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}instance\_type{\textquotedbl}}}\texttt{\textcolor{black}{
value=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}uk.ac.ic.doc.neuralnets.graph.neural.Synapse{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{meta:properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{properties}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{connection}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{connections}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{projection}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{projections}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{networkml}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}
\\\hline
\end{longtable}
{\raggedleft\itshape
Code 1: Example network in NeuroML (XML) format.
\par}

\begin{longtable}[c]{|p{14.8cm}|}
\hline
\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}?xml}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.2,0.47843137,0.5294118}{version}}\texttt{\textcolor{black}{=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1.0{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.2,0.47843137,0.5294118}{encoding}}\texttt{\textcolor{black}{=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}UTF{}-8{\textquotedbl}}}\texttt{\textcolor{black}{?}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{X3D
profile=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Immersive..{\textquotedbl}}}\texttt{\textcolor{black}{
}}\texttt{\textcolor[rgb]{0.2,0.47843137,0.5294118}{version}}\texttt{\textcolor{black}{=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2.0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Scene}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Background
skyColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.6
0.7
0.9{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Viewpoint
description=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Down
z axis, 500 microns away{\textquotedbl}}}\texttt{\textcolor{black}{
position=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
0
500{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Viewpoint
description=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Down
z axis, 200 microns away{\textquotedbl}}}\texttt{\textcolor{black}{
position=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
0
200{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Viewpoint
description=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}Down
z axis, 2mm away{\textquotedbl}}}\texttt{\textcolor{black}{
position=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
0
2000{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
rotation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
0 1
{}-1.570795{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cylinder
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}200{\textquotedbl}}}\texttt{\textcolor{black}{
radius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.5{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
translation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
105
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cone
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}10{\textquotedbl}}}\texttt{\textcolor{black}{
bottomRadius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}\texttt{\textcolor{black}{
\ \ \ }}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cylinder
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}200{\textquotedbl}}}\texttt{\textcolor{black}{
radius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.5{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
translation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
105
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cone
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}10{\textquotedbl}}}\texttt{\textcolor{black}{
bottomRadius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
rotation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1
0 0
1.570795{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1
0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cylinder
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}200{\textquotedbl}}}\texttt{\textcolor{black}{
radius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0.5{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
translation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
105
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1
0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Cone
height=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}10{\textquotedbl}}}\texttt{\textcolor{black}{
bottomRadius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}1{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
translation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}73
\ 26
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Sphere
radius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}5{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform
translation=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}456
\ 292
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material
diffuseColor=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Sphere
radius=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}5{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.13725491,0.43137255,0.14509805}{{\textless}!{}-{}-Projection
Network{}-Synapses between 14 and 14{}-{}-{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{LineSet
vertexCount=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Coordinate
point=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}73
\ 26 \ 0, 73 \ 26
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Color
color=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1 0, 1 0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{LineSet}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}\texttt{\textcolor{black}{
\ }}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}
\\
\end{longtable}
\begin{longtable}[c]{|p{14.8cm}|}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{LineSet
vertexCount=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Coordinate
point=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}456
\ 292 \ 0, 456 \ 292
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Color
color=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1 0, 1 0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{LineSet}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{LineSet
vertexCount=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Coordinate
point=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}73
\ 26 \ 0, 456 \ 292
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Color
color=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1 0, 1 0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{LineSet}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Material}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Appearance}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{LineSet
vertexCount=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}2{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Coordinate
point=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}456
\ 292 \ 0, 73 \ 26
\ 0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}}}\texttt{\textcolor{black}{Color
color=}}\texttt{\textcolor[rgb]{0.5019608,0.07058824,0.7019608}{{\textquotedbl}0
1 0, 1 0
0{\textquotedbl}}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{/{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{LineSet}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Shape}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ \ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Transform}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor{black}{\ \ }}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{Scene}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}

\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textless}/}}\texttt{\textcolor{black}{X3D}}\texttt{\textcolor[rgb]{0.6509804,0.09019608,0.0}{{\textgreater}}}
\\\hline
\end{longtable}
{\raggedleft\itshape
Code 2: Example network in X3D (XML) format.
\par}


\bigskip

\begin{longtable}[c]{|p{14.8cm}|}
\hline
{\ttfamily
13,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,}

{\ttfamily
13,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,}

{\ttfamily
13,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,}

{\ttfamily
14,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,13}

{\ttfamily
14,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,}

{\ttfamily
14,uk.ac.ic.doc.neuralnets.graph.neural.NeuralNetwork,@@,}

{\ttfamily
16,uk.ac.ic.doc.neuralnets.graph.neural.SpikingNeurone,@@postSpikeReset={}-56.17718294810968@@z=0@@recoverySensitivity=0.2@@recoveryScale=0.02@@x=73@@trigger=30.0@@charge={}-65.0@@y=26@@pSRRecovery=4.0027868923975625@@,14}

{\ttfamily
15,uk.ac.ic.doc.neuralnets.graph.neural.SpikingNeurone,@@postSpikeReset={}-58.618716832163614@@z=0@@recoverySensitivity=0.2@@recoveryScale=0.02@@x=456@@trigger=30.0@@charge={}-65.0@@y=292@@pSRRecovery=4.551832219630733@@,14}

{\ttfamily
17,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,14}

{\ttfamily
17,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,16:16:{}-1}

{\ttfamily
17,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,16:16:{}-1}

{\ttfamily
19,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,14}

{\ttfamily
19,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,15:16:{}-1}

{\ttfamily
19,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,15:16:{}-1}

{\ttfamily
18,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,14}

{\ttfamily
18,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,16:15:{}-1}

{\ttfamily
18,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,16:15:{}-1}

{\ttfamily
20,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,14}

{\ttfamily
20,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,15:15:{}-1}

{\ttfamily
20,uk.ac.ic.doc.neuralnets.graph.neural.Synapse,@@,15:15:{}-1}
\\\hline
\end{longtable}
{\raggedleft\mdseries\itshape
Code 3: Example network in Text Network Serializer format.
\par}


\bigskip


\bigskip


\bigskip

\clearpage{\bfseries\upshape
Persistence Performance}


\bigskip

{\mdseries\upshape
Networks were generated with the number of excitatory spiking neurones
as specified in the table and a 100\% connectivity probability,
networks were regenerated when changing between sizes.}


\bigskip

{\bfseries\itshape
\textmd{\textup{Benchmarking }}\textmd{\textup{System:}}}

\liststyleLii
\begin{itemize}
\item {\mdseries\upshape
CPU  {}- 2.33GHz Core 2 Duo}
\item {\mdseries\upshape
Memory  {}- 2GB, 667MHz DDR2}
\item {\mdseries\upshape
Hard Disk {}- 160GB, 5,400rpm, 16MB cache.}
\item \textmd{\textup{File System {}-
}}\foreignlanguage{english}{\textmd{\textup{Journaled}}}\textmd{\textup{
HFS+}}
\item {\mdseries\upshape
OS  {}- Mac OS X 10.5.6}
\end{itemize}

\bigskip

\begin{longtable}[c]{|p{2.799cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|}
\hline
{\centering
Network Size
\par}
&
{\centering
Java Serialization
\par}
&
{\centering
NeuroML (XML)
\par}
&
{\centering
TNS
\par}
&
{\centering
X3D
\par}
\\\hline
{\raggedleft
10
\par}
&
{\raggedleft\color{black}
0.01
\par}
&
{\raggedleft\color{black}
0.00
\par}
&
{\raggedleft\color{black}
0.00
\par}
&
{\raggedleft\color{black}
0.06
\par}
\\\hline
{\raggedleft
50
\par}
&
{\raggedleft
0.19
\par}
&
{\raggedleft
0.06
\par}
&
{\raggedleft
0.00
\par}
&
{\raggedleft
0.48
\par}
\\\hline
{\raggedleft
100
\par}
&
{\raggedleft
0.74
\par}
&
{\raggedleft
0.65
\par}
&
{\raggedleft
0.00
\par}
&
{\raggedleft
4.25
\par}
\\\hline
{\raggedleft
500
\par}
&
{\raggedleft
16.97
\par}
&
{\raggedleft
5.43
\par}
&
{\raggedleft
4.27
\par}
&

\bigskip
\\\hline
{\raggedleft
1000
\par}
&
{\raggedleft
74.33
\par}
&
{\raggedleft
19.95
\par}
&
{\raggedleft
24.36
\par}
&

\bigskip
\\\hline
\end{longtable}
{\raggedleft\itshape
Table 1: Persistence Performance Analysis {}- Save Execution Time
\par}


\bigskip

\begin{longtable}[c]{|p{3.55cm}|p{3.55cm}|p{3.55cm}|p{3.55cm}|}
\hline
{\centering
Network Size
\par}
&
{\centering
Java Serialization
\par}
&
{\centering
NeuroML (XML)
\par}
&
{\centering
TNS
\par}
\\\hline
{\raggedleft
10
\par}
&
{\raggedleft\color{black}
0.06
\par}
&
{\raggedleft\color{black}
0.15
\par}
&
{\raggedleft\color{black}
0.05
\par}
\\\hline
{\raggedleft
50
\par}
&
{\raggedleft
0.35
\par}
&
{\raggedleft
0.41
\par}
&
{\raggedleft
0.23
\par}
\\\hline
{\raggedleft
100
\par}
&
{\raggedleft
1.01
\par}
&
{\raggedleft
0.71
\par}
&
{\raggedleft
0.69
\par}
\\\hline
{\raggedleft
500
\par}
&
{\raggedleft
23.37
\par}
&
{\raggedleft
11.21
\par}
&
{\raggedleft
20.29
\par}
\\\hline
{\raggedleft
1000
\par}
&
{\raggedleft
94.67
\par}
&
{\raggedleft
57.14
\par}
&
{\raggedleft
2091.74
\par}
\\\hline
\end{longtable}
{\raggedleft\itshape
Table 2: Persistence Performance Analysis {}- Load Execution Time
\par}


\bigskip

\begin{longtable}[c]{|p{2.799cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|}
\hline
{\centering
Network Size
\par}
&
{\centering
Java Serialization
\par}
&
{\centering
NeuroML (XML)
\par}
&
{\centering
TNS
\par}
&
{\centering
X3D
\par}
\\\hline
{\raggedleft
10
\par}
&
{\raggedleft\color{black}
11196
\par}
&
{\raggedleft\color{black}
37893
\par}
&
{\raggedleft\color{black}
14192
\par}
&
{\raggedleft\color{black}
21528
\par}
\\\hline
{\raggedleft
50
\par}
&
{\raggedleft
190396
\par}
&
{\raggedleft
784778
\par}
&
{\raggedleft
311878
\par}
&
{\raggedleft
476128
\par}
\\\hline
{\raggedleft
100
\par}
&
{\raggedleft
733896
\par}
&
{\raggedleft
3065153
\par}
&
{\raggedleft
1230880
\par}
&
{\raggedleft
1885870
\par}
\\\hline
{\raggedleft
500
\par}
&
{\raggedleft
17861896
\par}
&
{\raggedleft
74209903
\par}
&
{\raggedleft
33611758
\par}
&

\bigskip
\\\hline
{\raggedleft
1000
\par}
&
{\raggedleft
71221896
\par}
&
{\raggedleft
296670598
\par}
&
{\raggedleft
125334485
\par}
&

\bigskip
\\\hline
\end{longtable}
{\raggedleft\itshape
Table 3: Persistence Peformance Analysis {}- File Size
\par}


\bigskip

{\upshape
\textbf{\textit{Note:}} Graphs depicting the information in the above
tables can be found on the following page.}


\bigskip

{\upshape
The obvious first point is that X3D failed to successfully produce any
output on networks of size 500 and 1000, after further debugging the
problem lies with the Java XML Transformer which is incapable from
transforming large XML documents. Also because of the implementation,
nearly twice as much storage is required during export, as the XML
document needs to be produced so that it can then be read and can only
be deleted after completion. Its clear that a future release of the X3D
plug{}-in should be implemented in a more efficient way.}


\bigskip

{\upshape
NeuroML and Serialization grow linearly on a logarithmic graph for Save
and Loading time suggesting that their execution time would predictably
grow with larger networks and would be easily estimated with network
sizes within the range of network sizes sampled. NeuroML does generally
perform better than Java Serialization, especially with large networks,
however this is offset by NeuroML having a considerably larger
resulting file size than Serialization, which with ever increasing
networks would start to cause problems, an option of compressing the
output of the text based persistence methods could provide further
persistence options to the user.}

\clearpage{\mdseries\upshape
}

\begin{center}
\begin{minipage}{17cm}
{\raggedleft\itshape
 [Warning: Image not found] Graph 1: Performance Analysis Graphs
\par}
\end{minipage}\end{center}
{\mdseries\upshape
TNS has some interesting cases, firstly that for networks below 100
neurones in it requires significantly less time than all other
persistence methods and requires no more time for up to 100. After this
it rises sharply but looks to begin levelling out to the same rate of
increase as NeuroML and Serialization. File sizes generated are less
than NeuroML but not as small as Serialization and the load time is
good, but insignificantly different from serialization or NeuroML.}


\bigskip

{\mdseries\upshape
A performance metric was calculated that took into account the loading
and save times, as well as the file size generated, compared to the
network being persisted. The performance metric was as follows:}


\bigskip

{\mdseries\upshape
 $\text{Performance Metric}=\frac{\text{Load Time}+\text{Save
Time}}{\text{File Size}}$ }


\bigskip

{\mdseries\upshape
A lower value implies better peformance, as we can see from the graph
which plots the metric against the network size that Java Serialization
is the obvious winning, that was to be expected as even though it has a
poor saving time it produces significantly smaller files than the other
persistence methods and requires no extra time for loading. TNS and
NeuroML look to be improving after reaching an initial storage overhead
on network size, TNS beating NeuroML though because of the smaller file
sizes produced. X3D was included for completeness, but now real
information can be taken from the graph as X3D has no load time and
could not complete all the tests.}


\bigskip

{\mdseries\upshape
Its worth noting that this performance analysis was only a fleeting look
at persistences real world performance and tests were only run once
instead of multiple times to verify results. This means little more
statistical analysis can be done on these results as there
isn't the required information.}

\clearpage{\bfseries\upshape
Persistence Evaluation and Further Development}


\bigskip

{\mdseries\upshape
The Persistence module provides an easy and extensible way of
implementing persistence plug{}-ins which can export the neural network
model to storage or possibly another application. The initial
persistence plug{}-ins provide the average user with a number of
options for saving and exporting, with Java Serialization the recommend
method for saving a neural network for use with other instances of the
ANNE application or incremental backup. NeuroML export is available for
transferring your network to other applications and importing back from
it.}


\bigskip

{\mdseries\upshape
Due to the plug{}-in nature, further version of a persistence option
would not require to be released at the same time as the core
framework, allowing for them to be worked on and released separately.
New persistence options could be added later on if required for
exporting to more specific or propriety formats, this would allow
developers of other applications, perhaps closed{}-source to write
their own plug{}-in to read their application output which could be
distributed without having to reveal a specification of their file
format. This ease of implementation would hopefully help ANNE become a
more popular solution to model neural networks with.}


\bigskip

{\mdseries\upshape
Further development other persistence could include:}

\liststyleLiii
\begin{itemize}
\item {\mdseries\upshape
Further performance analysis of all the persistence plug{}-in and
optimizations of their code to improve execution time and memory
usage.}
\item {\mdseries\upshape
The option for file compression after export would reduce the file sizes
produced but obviously at a cost of execution time. There may be a
point where a network reaches a certain size that it may be necessary
to compress the output file, already with 1000 neurones, NeuroML files
reach 280MB, which even with current hard drive capacities is a large
file. With the option to saved to a compressed format, automatic
decompression of files when loading would be required so that the new
compressed files where supported. Perhaps a flag in each persistence
plug{}-in for compression with compression itself being another
persistence plug{}-in.}
\item {\mdseries\upshape
X3D's current implementation is incapable of exporting
large networks because of the problems using XSL transformation on
large XML documents. A bespoke plug{}-in which is not dependent on the
NeuroML plug{}-in would probably be the best implementation. Also this
would reduce the amount of storage required for export as currently an
XML must be produced before being read again and then deleted.}
\item {\mdseries\upshape
Further persistence options such as exporting to other neural network
modelling standards and file formats such as the previously mentions
PyNN and Mat{}-labs Neural Network tool.}
\item {\mdseries\upshape
An auto{}-save feature would be a positive addition, meaning that users
aren't required to remember to periodically save their
work, incase of mistake or system failure. It could be implemented by
creating another thread which sleeps for the auto{}-save time period
and then fires the save manager off before sleeping again.}
\end{itemize}
\end{document}
